Approximation as Differentiation: Notes

### 2025-05-16 notes/preliminaries.tex
Notation for PSh(C) and PSc_V(C).

\paragraph{Coproduct and product of morphisms.} In a category with coproducts $X + Y$ or products $X \times
Y$, we write:
\begin{itemize}
\item $\coprodM{f}{g}: X + Y \to Z$ for the coproduct of morphisms $f: X \to Z$ and $g: Y \to Z$
\item $\prodM{f}{g}: X \to Y \times Z$ for the product of morphisms $f: X \to Y$ and $g: X \to Z$
\item $(f,g): X \times Y \to Z \times W$ for $\prodM{f \comp \proj_1}{g \comp \proj_2}$ where $f: X \to Z$ and $g: Y \to W$.
\end{itemize}

@@

>>>>

\paragraph{Coproduct and product of morphisms.} In a category with coproducts $X + Y$ or products $X \times
Y$, we write:
\begin{itemize}
\item $\coprodM{f}{g}: X \coprod Y \to Z$ for the coproduct of morphisms $f: X \to Z$ and $g: Y \to Z$
\item $\prodM{f}{g}: X \to Y \times Z$ for the product of morphisms $f: X \to Y$ and $g: X \to Z$
\item $(f,g): X \times Y \to Z \times W$ for $\prodM{f \comp \proj_1}{g \comp \proj_2}$ where $f: X \to Z$ and $g: Y \to W$.
\end{itemize}

@@

\subsubsection{Presheaves and $\mathscr{V}$-enriched presheaves}

Write:
\begin{itemize}
\item $\PSh(C)$ for the category of presheaves $\Func{C^\op}{\Set}$
\item $\PSh_{\mathscr{V}}(C)$ for the category of $\mathscr{V}$-enriched presheaves
$\Func{C^\op}{\mathscr{V}}$.
\end{itemize}
